---
title: "R Notebook"
output: html_notebook
---

```{r libraries}
library(tidyverse)
```


```{r data}
townsville_complaints <- read_csv("data/animal_complaints.csv")
brisbane_complaints <- read_csv("data/brisbane_complaints.csv")
rspca_outcomes <- read_csv("data/animal_outcomes.csv")
```


```{r cleaning}
states <- quote(c(act,nsw,nt,qld,sa,tas,vic,wa))
outcomes <- quote(c(reclaimed, rehomed, other, euthanized, released, in_stock, transferred, currently_in_care))
lrr_outcomes <- quote(c(reclaimed, rehomed, euthanized, released, in_stock, transferred))

rspca_clean <- rspca_outcomes %>% 
  janitor::clean_names() %>% 
  group_by(year, animal_type, outcome) %>% 
  mutate(total = sum(!!states, na.rm = TRUE)) %>% 
  ungroup()

# The LRR is the percentage of animals who were rehomed, reclaimed by their owner or transferred to a
# rescue group or other non-RSPCA facility as a percentage of the total number of animals received (not
# including those currently in care or categorised as ‘other’)

rspca_summary <- rspca_clean %>% 
  pivot_wider(names_from = outcome, 
              values_from = total, 
              id_cols = c(year, animal_type), 
              names_glue = '{snakecase::to_snake_case(outcome)}') %>% 
  group_by(year, animal_type) %>% 
  mutate(total = sum(!!outcomes, na.rm = TRUE),
         lrr_total = sum(!!lrr_outcomes, na.rm = TRUE)) %>% 
  mutate(success = round((sum(reclaimed, rehomed, released, na.rm = TRUE) / total), 2),
         lrr = round((sum(reclaimed, rehomed, released, transferred, na.rm = TRUE) / lrr_total), 2))

rspca_states <- rspca_clean %>% 
  select(-total) %>% 
  pivot_longer(act:wa, 
               values_to = "count", 
               names_to = "state", 
               names_transform = list(state = toupper)) %>% 
  pivot_wider(names_from = outcome, 
              values_from = count, 
              names_glue = '{snakecase::to_snake_case(outcome)}') %>% 
  group_by(year, animal_type, state) %>% 
  mutate(total = sum(!!outcomes, na.rm = TRUE),
         lrr_total = sum(!!lrr_outcomes, na.rm = TRUE)) %>% 
  mutate(success = round((sum(reclaimed, rehomed, released, na.rm = TRUE) / total), 2),
         lrr = round((sum(reclaimed, rehomed, released, transferred, na.rm = TRUE) / lrr_total), 2))

rspca_totals <- rspca_clean %>% 
  group_by(year, animal_type) %>% 
  summarise(act = sum(act),
            nsw = sum(nsw),
            nt = sum(nt),
            qld = sum(qld),
            sa = sum(sa),
            tas = sum(tas),
            vic = sum(vic),
            wa = sum(wa))

rspca_state_totals <- rspca_totals %>% 
  pivot_longer(cols = c(act:wa), names_transform = toupper, names_to = "state", values_to = "count")

brisbane_clean <- brisbane_complaints %>% 
  select(-c(nature, responsible_office, city)) %>% 
  mutate(category = replace_na(category, "Not Provided"),
         date_range = str_remove_all(date_range, "(.csv)|(.*(?=(jan)|(apr)|(oct)))"),
         date_range = str_replace_all(date_range, "(^january)|(^1st)|(^jan)", "Q1"),
         date_range = str_replace_all(date_range, "(^april)|(^apr)", "Q2"),
         date_range = str_replace_all(date_range, "(^july)|(^jul)", "Q3"),
         date_range = str_replace_all(date_range, "(^october)|(^oct)", "Q4"),
         date_range = str_replace(date_range, "-.*-"," "),
         date_range = str_replace(date_range, "Q1 17", "Q1 2016"),
         category = if_else(animal_type == "Cat Trapping", "Cat Trapping", category),
         animal_type = if_else(animal_type == "Cat Trapping", "Cat", animal_type),
         suburb = snakecase::to_title_case(suburb),
         date_range = factor(date_range, levels = c("Q1 2016", "Q2 2016", "Q3 2016", "Q4 2016",
                                                    "Q1 2017", "Q2 2017", "Q3 2017", "Q4 2017",
                                                    "Q1 2018", "Q2 2018", "Q3 2018", "Q4 2018",
                                                    "Q1 2019", "Q2 2019", "Q3 2019", "Q4 2019",
                                                    "Q1 2020", "Q2 2020"
         ))
  ) %>% 
  separate(date_range, c("quarter", "year"), remove = FALSE) %>% 
  relocate(date_range, .before = animal_type)

townsville_clean <- townsville_complaints %>% 
  janitor::clean_names() %>%
  group_by(date_received) %>% 
  separate(date_received, c("month", "year"), sep = " ", remove = FALSE) %>% 
  mutate(month = factor(month, levels = c("January", "February","March","April","May","June",
                                          "July","August","September","October","November","December")),
         quarter = case_when(
           month %in% c("January", "February", "March") ~ "Q1",
           month %in% c("April", "May", "June") ~ "Q2",
           month %in% c("July", "August", "September") ~ "Q3",
           TRUE ~ "Q4"
         )) %>% 
  relocate(c("year", "month"), .before = quarter) %>% 
  unite("date_range", c(quarter, year), sep = " ", remove = FALSE) %>% 
  mutate(date_range = factor(date_range, levels = c("Q4 2013",
                                                    "Q1 2014", "Q2 2014", "Q3 2014", "Q4 2014",
                                                    "Q1 2015", "Q2 2015", "Q3 2015", "Q4 2015",
                                                    "Q1 2016", "Q2 2016", "Q3 2016", "Q4 2016",
                                                    "Q1 2017", "Q2 2017", "Q3 2017", "Q4 2017",
                                                    "Q1 2018", "Q2 2018", "Q3 2018", "Q4 2018",
                                                    "Q1 2019", "Q2 2019", "Q3 2019", "Q4 2019",
                                                    "Q1 2020", "Q2 2020")))
```

```{r ggplot theme}
mytheme <- theme_classic() +
  theme(legend.position = "bottom",
        legend.title = element_blank(),
        legend.background = element_rect(fill = "grey88", colour = "black"),
        legend.key = element_rect())
```


# RSPCA

Everything except Wildlife -

Currently in Care is incomplete - starts in 2009
In stock only exists for 2002 - 2008
Transferred is incomplete - starts in 2002

Wildlife
Different stats --
No Reclaimed, Rehome
Has Released
Rest the same

Can do euthanization comparisons across them all. 

The LRR is the percentage of animals who were rehomed, reclaimed by their owner or transferred to a rescue group or other non-RSPCA facility as a percentage of the total number of animals received (not including those currently in care or categorised as ‘other’)

```{r RSPCA reportage}
rspca_states %>% 
  filter(animal_type == "Dogs", year >= 2002) %>% 
  ggplot(aes(x = year, y = success, col = state, group = state)) +
  geom_line(size = 1) +
  scale_y_continuous(labels = scales::percent,
                     breaks = seq(0, 1, 0.05)) +
  scale_x_continuous(breaks = seq(2002, 2022, 1)) +
  labs(title = "Percentage of Dogs Adopted or Reclaimed, 2002 - 2018",
       y = "% of Dogs",
       x = "Year") +
  mytheme +
  guides(color = guide_legend(nrow = 1, override.aes = list(linewidth = 1.5))) +
  theme(legend.key.width = unit(1, "cm")) +
  scale_color_brewer(palette = "Dark2")

rspca_states %>% 
  filter(animal_type == "Dogs", year >= 2002) %>% 
  ggplot(aes(x = year, y = lrr, col = state, group = state)) +
  geom_line(size = 1) +
  scale_y_continuous(labels = scales::percent,
                     breaks = seq(0, 1, 0.05)) +
  scale_x_continuous(breaks = seq(2002, 2022, 1)) +
  labs(title = "Live Release Rate (LRR) of Dogs, 2002 - 2018",
       y = "% of Dogs",
       x = "Year") +
  mytheme +
  guides(color = guide_legend(nrow = 1, override.aes = list(linewidth = 1.5))) +
  theme(legend.key.width = unit(1, "cm")) +
  scale_color_brewer(palette = "Dark2")

rspca_states %>% 
  filter(animal_type == "Cats", year >= 2002) %>% 
  ggplot(aes(x = year, y = success, col = state, group = state)) +
  geom_line(size = 1) +
  scale_y_continuous(labels = scales::percent,
                     breaks = seq(0, 1, 0.05)) +
  scale_x_continuous(breaks = seq(2002, 2022, 1)) +
  labs(title = "Percentage of Cats Adopted or Reclaimed, 2002 - 2018",
       y = "% of Cats",
       x = "Year") +
  mytheme +
  guides(color = guide_legend(nrow = 1, override.aes = list(linewidth = 1.5))) +
  theme(legend.key.width = unit(1, "cm")) +
  scale_color_brewer(palette = "Dark2")

rspca_states %>% 
  filter(animal_type == "Cats", year >= 2002) %>% 
  ggplot(aes(x = year, y = lrr, col = state, group = state)) +
  geom_line(size = 1) +
  scale_y_continuous(labels = scales::percent,
                     breaks = seq(0, 1, 0.05)) +
  scale_x_continuous(breaks = seq(2002, 2022, 1)) +
  labs(title = "Live Release Rate (LRR) of Cats, 2002 - 2018",
       y = "% of Cats",
       x = "Year") +
  mytheme +
  guides(color = guide_legend(nrow = 1, override.aes = list(linewidth = 1.5))) +
  theme(legend.key.width = unit(1, "cm")) +
  scale_color_brewer(palette = "Dark2")

rspca_clean %>% 
  filter(year >= 2009,
         outcome != "In Stock") %>% 
  ggplot(aes(x = year, y = total, fill = outcome)) +
  geom_bar(position = "fill", stat = "identity" ) +
  scale_y_continuous(labels = scales::percent) +
  scale_x_continuous(breaks = seq(2009, 2022, 1)) +
  labs(title = "Proportion of All Outcomes in RSPCA Shelters, 2009 - 2018",
       y = "% of Animals",
       x = "Year") +
  mytheme +
  guides(fill=guide_legend(nrow=2, override.aes = list(colour = "black",
                                                       size = 0.1))) +
  scale_fill_brewer(palette = "Set1")

rspca_clean %>% 
  filter(animal_type == "Dogs", year >= 2009,
         outcome != "In Stock") %>% 
  ggplot(aes(x = year, y = total, fill = outcome)) +
  geom_bar(position = "fill", stat = "identity" ) +
  scale_y_continuous(labels = scales::percent) +
  scale_x_continuous(breaks = seq(2009, 2022, 1)) +
  labs(title = "Proportion of Dog Outcomes in RSPCA Shelters, 2009 - 2018",
       y = "% of Dogs",
       x = "Year") +
  mytheme +
  guides(fill=guide_legend(nrow=1, override.aes = list(colour = "black",
                                                       size = 0.1))) +
  scale_fill_brewer(palette = "Set1")

rspca_clean %>% 
  filter(animal_type == "Cats", year >= 2009,
         outcome != "In Stock") %>% 
  ggplot(aes(x = year, y = total, fill = outcome)) +
  geom_bar(position = "fill", stat = "identity" ) +
  scale_y_continuous(labels = scales::percent) +
  scale_x_continuous(breaks = seq(2009, 2022, 1)) +
  labs(title = "Proportion of Cat Outcomes in RSPCA Shelters, 2009 - 2018",
       y = "% of Cats",
       x = "Year") +
  mytheme +
  guides(fill=guide_legend(nrow=1, override.aes = list(colour = "black",
                                                       size = 0.1))) +
  scale_fill_brewer(palette = "Set1")

rspca_clean %>% 
  filter(animal_type == "Wildlife", year >= 2009,
         outcome != "In Stock") %>% 
  ggplot(aes(x = year, y = total, fill = outcome)) +
  geom_bar(position = "fill", stat = "identity" ) +
  scale_y_continuous(labels = scales::percent) +
  scale_x_continuous(breaks = seq(2009, 2022, 1)) +
  labs(title = "Proportion of Wildlife Outcomes in RSPCA Shelters, 2009 - 2018",
       y = "% of Wildlife",
       x = "Year") +
  mytheme +
  guides(fill=guide_legend(nrow=1, override.aes = list(colour = "black",
                                                       size = 0.1))) +
  scale_fill_brewer(palette = "Set1")

rspca_clean %>% 
  ggplot(aes(x = year, y = total, fill = animal_type)) +
  geom_bar(position = "fill", stat = "identity" ) +
  scale_y_continuous(labels = scales::percent) +
  scale_x_continuous(breaks = seq(1999, 2018, 1)) +
  labs(title = "Proportion of Received Animals in RSPCA Shelters, 1999 - 2018",
       y = "% of Animals",
       x = "Year") +
  mytheme +
  guides(fill=guide_legend(nrow=1, override.aes = list(colour = "black",
                                                       size = 0.1))) +
  scale_fill_brewer(palette = "Dark2")

rspca_clean %>% 
  ggplot(aes(x = year, y = total, fill = st)) +
  geom_bar(position = "fill", stat = "identity" ) +
  scale_y_continuous(labels = scales::percent) +
  scale_x_continuous(breaks = seq(1999, 2018, 1)) +
  labs(title = "Proportion of Received Animals in RSPCA Shelters, 1999 - 2018",
       y = "% of Animals",
       x = "Year") +
  mytheme +
  guides(fill=guide_legend(nrow=1, override.aes = list(colour = "black",
                                                       size = 0.1))) +
  scale_fill_brewer(palette = "Dark2")

rspca_summary %>% 
  filter(year >= 2009, animal_type == "Dogs") %>% 
  ggplot(aes(x = year)) +
  geom_line(aes(y = lrr, colour = "Live Release"), size = 1) +
  geom_line(aes(y = success, colour = "Adopted / Reclaimed"), size = 1) +
  scale_y_continuous(labels = scales::percent,
                     breaks = seq(0, 1, 0.02)) +
  scale_x_continuous(breaks = seq(2009, 2022, 1)) +
  labs(title = "Dogs Adopted or Reclaimed and Live Release Rate (LRR), 2009 - 2018",
       y = "% of Dogs",
       x = "Year") +
  mytheme +
  guides(color = guide_legend(nrow = 1, override.aes = list(linewidth = 1.5))) +
  theme(legend.key.width = unit(1, "cm")) +
  scale_colour_manual(values = c("darkorchid", "deepskyblue2"),
                      limits = c("Live Release", "Adopted / Reclaimed"))

rspca_summary %>% 
  filter(year >= 2009, animal_type == "Cats") %>% 
  ggplot(aes(x = year)) +
  geom_line(aes(y = lrr, colour = "Live Release"), size = 1) +
  geom_line(aes(y = success, colour = "Adopted / Reclaimed"), size = 1) +
  scale_y_continuous(labels = scales::percent,
                     breaks = seq(0, 1, 0.05)) +
  scale_x_continuous(breaks = seq(2009, 2022, 1)) +
  labs(title = "Cats Adopted or Reclaimed and Live Release Rate (LRR), 2009 - 2018",
       y = "% of Cats",
       x = "Year") +
  mytheme +
  guides(color = guide_legend(nrow = 1, override.aes = list(linewidth = 1.5))) +
  theme(legend.key.width = unit(1, "cm")) +
  scale_colour_manual(values = c("darkorchid", "deepskyblue2"),
                      limits = c("Live Release", "Adopted / Reclaimed"))

rspca_summary %>% 
  filter(year >= 2009, animal_type == "Wildlife") %>% 
  ggplot(aes(x = year)) +
  geom_line(aes(y = lrr, colour = "Live Release"), size = 1) +
  geom_line(aes(y = success, colour = "Released"), size = 1) +
  scale_y_continuous(labels = scales::percent,
                     breaks = seq(0, 1, 0.05)) +
  scale_x_continuous(breaks = seq(2009, 2022, 1)) +
  labs(title = "Wildlife Released and Live Release Rate (LRR), 2009 - 2018",
       y = "% of Cats",
       x = "Year") +
  mytheme +
  guides(color = guide_legend(nrow = 1, override.aes = list(linewidth = 1.5))) +
  theme(legend.key.width = unit(1, "cm")) +
  scale_colour_manual(values = c("darkorchid", "deepskyblue2"),
                      limits = c("Live Release", "Released"))

rspca_summary %>% 
  filter(year >= 2009, animal_type %in% c("Dogs", "Cats")) %>% 
  ggplot(aes(x = year)) +
  geom_line(aes(y = lrr, colour = animal_type), size = 1) +
  scale_y_continuous(labels = scales::percent,
                     breaks = seq(0, 1, 0.05)) +
  scale_x_continuous(breaks = seq(2009, 2022, 1)) +
  labs(title = "Dog and Cat Live Release Rates (LRR), 2009 - 2018",
       y = "% of Animals",
       x = "Year") +
  mytheme +
  guides(color = guide_legend(nrow = 1, override.aes = list(linewidth = 1.5))) +
  theme(legend.key.width = unit(1, "cm")) +
  scale_colour_manual(values = c("aquamarine3", "chocolate1"),
                      limits = c("Cats", "Dogs"))

rspca_outcomes %>%
  filter(outcome == "Euthanized") %>% 
  ggplot(aes(x = year)) +
  geom_line(aes(y = Total, colour = animal_type), size = 1) +
  geom_vline(xintercept = 2007, linetype = "dotted") +
  scale_y_continuous(breaks = seq(0, 50000, 10000)) +
  scale_x_continuous(breaks = seq(1999, 2022, 2)) +
  labs(title = "Number of Animals Euthanised per Year at RSPCA Shelters, 1999 - 2018",
       y = "No. of Animals",
       x = "Year") +
  mytheme +
  guides(color = guide_legend(nrow = 1, override.aes = list(linewidth = 1.5))) +
  theme(legend.key.width = unit(1, "cm")) +
  scale_fill_brewer(palette = "Set1")

rspca_summary %>%
  group_by(year) %>% 
  select(year, euthanized) %>% 
  summarise(total = sum(euthanized)) %>% 
  ggplot(aes(x = year)) +
  geom_line(aes(y = total), group = 1, size = 1, colour = "dodgerblue1") +
  geom_vline(xintercept = 2007, linetype = "dotted") +
  scale_y_continuous(breaks = seq(0, 100000, 5000)) +
  scale_x_continuous(breaks = seq(1999, 2022, 2)) +
  labs(title = "Number of Animals Euthanised per Year at RSPCA Shelters, 1999 - 2018",
       y = "No. of Animals",
       x = "Year") +
  mytheme +
  guides(color = guide_legend(nrow = 1, override.aes = list(linewidth = 1.5))) +
  theme(legend.key.width = unit(1, "cm")) +
  scale_fill_brewer(palette = "Set1")
```
```{r}
rspca_states %>% 
  ggplot(aes(x = year, y = total, fill = state)) +
  geom_bar(position = "fill", stat = "identity" ) +
  scale_y_continuous(labels = scales::percent) +
  scale_x_continuous(breaks = seq(1999, 2018, 1)) +
  labs(title = "Proportion of Received Animals in RSPCA Shelters by State, 1999 - 2018",
       y = "% of Animals",
       x = "Year") +
  mytheme +
  guides(fill=guide_legend(nrow=1, override.aes = list(colour = "black",
                                                       size = 0.1))) +
  scale_fill_brewer(palette = "Dark2")

rspca_states %>% 
  ggplot(aes(x = year, y = euthanized, fill = state)) +
  geom_bar(position = "fill", stat = "identity" ) +
  scale_y_continuous(labels = scales::percent) +
  scale_x_continuous(breaks = seq(1999, 2018, 1)) +
  labs(title = "Proportion of Euthanized Animals in RSPCA Shelters by State, 1999 - 2018",
       y = "% of Animals",
       x = "Year") +
  mytheme +
  guides(fill=guide_legend(nrow=1, override.aes = list(colour = "black",
                                                       size = 0.1))) +
  scale_fill_brewer(palette = "Dark2")

rspca_states %>% 
  group_by(year, state) %>% 
  select(year, state, euthanized) %>% 
  summarise(euthanized = sum(euthanized))
```


# Brisbane

MISSING Q3 2016. ENDS Q2 2020
Category for Other Animal sometimes lists what the animal is

```{r}
brisbane_clean %>% 
  filter(animal_type == "Cat") %>% 
  group_by(category) %>% 
  summarise(count = n()) %>% 
  arrange(-count)

brisbane_clean %>% 
  filter(animal_type == "Other Animal") %>% 
  group_by(category) %>% 
  summarise(count = n()) %>% 
  arrange(-count)

brisbane_clean %>% 
  filter(animal_type == "Attack") %>% 
  group_by(category) %>% 
  summarise(count = n()) %>% 
  arrange(-count)

brisbane_clean %>% 
  filter(animal_type == "Attack") %>% 
  group_by(year) %>% 
  summarise(count = n()) %>% 
  arrange(-count)

brisbane_clean %>% 
  filter((year == 2016 & quarter == "Q4") | year > 2016) %>%
  group_by(date_range, suburb) %>% 
  summarise(count = n()) %>% 
  slice_max(count, n = 3)

brisbane_clean %>% 
  filter((year == 2016 & quarter == "Q4") | year > 2016) %>%
  group_by(date_range, animal_type) %>% 
  summarise(count = n()) %>% 
  slice_max(count, n = 3)

brisbane_clean %>% 
  filter((year == 2016 & quarter == "Q4") | year > 2016) %>%
  group_by(date_range, suburb, animal_type) %>% 
  summarise(count = n()) %>% 
  slice_max(count) %>% 
  arrange(date_range, -count) %>% 
  group_by(date_range) %>% 
  slice_max(count, n = 3)

brisbane_clean %>% 
  filter(year > 2016) %>%
  group_by(year, suburb, animal_type) %>% 
  summarise(count = n()) %>% 
  slice_max(count) %>% 
  arrange(year, -count) %>% 
  group_by(year, animal_type) %>% 
  summarise(count = n()) %>% 
  arrange(year, -count)

brisbane_clean %>% 
  filter(year > 2016) %>%
  group_by(year, suburb, category) %>% 
  summarise(count = n()) %>% 
  slice_max(count) %>% 
  arrange(year, -count) %>% 
  group_by(year, category) %>% 
  summarise(count = n()) %>% 
  slice_max(count, n = 5) %>% 
  arrange(year, -count)

brisbane_clean %>% 
  filter(year > 2016 & animal_type != "Attack") %>% 
  group_by(year, quarter, animal_type) %>% 
  summarise(count = n(), .groups = "drop") %>% 
  ggplot(aes(x = quarter, y = count, colour = animal_type, group = animal_type)) +
  geom_line() +
  facet_wrap(~ year, scales = "free")

brisbane_clean %>% 
  filter((year == 2016 & quarter == "Q4") | year > 2016) %>%
  group_by(date_range) %>% 
  summarise(count = n(), .groups = "drop") %>% 
  ggplot(aes(x = date_range, y = count, group = 1)) +
  geom_line() +
  theme(axis.text.x = element_text(angle = 45))

brisbane_clean %>% 
  filter(year > 2016 & animal_type == "Other Animal") %>% 
  group_by(year, quarter, category) %>% 
  summarise(count = n(), .groups = "drop") %>% 
  ggplot(aes(x = quarter, y = count, colour = category, group = category)) +
  geom_line() +
  facet_wrap(~ year, scales = "free")
```

## Questions

### Total call volume for complaint calls, trend over time

```{r}
brisbane_clean %>%
  filter((year == 2016 & quarter == "Q4") | year > 2016) %>% 
  summarise(number_of_calls = n())

# by quarter

brisbane_clean %>%
  filter((year == 2016 & quarter == "Q4") | year > 2016) %>%
  group_by(date_range) %>% 
  summarise(count = n()) %>% 
  ggplot() +
  geom_line(aes(x = date_range, y = count, group = 1), linewidth = 1, colour = "chocolate1") +
  labs(title = "Total Call Volume, Animal Complaints, Brisbane Q4 2016 - Q2 2020",
       y = "No. of Calls",
       x = "Quarter, Year") +
  mytheme +
  scale_y_continuous(breaks = seq(1000, 3000, by = 250)) +
  theme(axis.text.x = element_text(angle = 45, 
                                   vjust = 1,
                                   hjust = 1
  ))

# by year, don't use this

# brisbane_clean %>%
#   filter(year > 2016 & year < 2020) %>%
#   group_by(year) %>% 
#   summarise(count = n()) %>% 
#   ggplot() +
#   geom_line(aes(x = year, y = count, group = 1))
```

### Particular call most common?

```{r}
brisbane_clean %>% 
  filter(((year == 2016 & quarter == "Q4") | year > 2016)) %>% 
  group_by(date_range, animal_type) %>% 
  summarise(count = n()) %>% 
  ggplot(aes(x = date_range, y = count, colour = animal_type, group = animal_type)) +
  geom_line(linewidth = 1) +
  labs(title = "Reasons for Complaint Calls, Brisbane Q4 2016 - Q2 2020",
       y = "No. of Calls",
       x = "Quarter, Year") +
  mytheme +
  scale_y_continuous(breaks = seq(0, 2000, by = 200)) +
  guides(color = guide_legend(nrow = 1, override.aes = list(linewidth = 1.5))) +
  theme(legend.key.width = unit(1, "cm")) +
  theme(axis.text.x = element_text(angle = 45, 
                                   vjust = 1,
                                   hjust = 1
  ))
```

### Huge dog spike -- what factor is driving this?

```{r}
brisbane_clean %>% 
  group_by(date_range, category, animal_type) %>%
  filter(((year == 2016 & quarter == "Q4") | year > 2016) & animal_type == "Dog") %>% 
  summarise(count = n()) %>% 
  select(-animal_type) %>% 
  arrange(date_range)

brisbane_clean %>% 
  group_by(date_range, category, animal_type) %>%
  filter(((year == 2016 & quarter == "Q4") | year > 2016) & animal_type == "Dog") %>%
  summarise(count = n()) %>% 
  filter(count > 5) %>% 
  ggplot(aes(x = date_range, y = count, colour = category, group = category)) +
  geom_line(linewidth = 1) +
  labs(title = "Reasons for Dog Complaint Calls, Brisbane Q4 2016 - Q2 2020",
       y = "No. of Calls",
       x = "Quarter, Year") +
  mytheme +
  scale_y_continuous(breaks = seq(0, 800, by = 50)) +
  guides(color = guide_legend(nrow = 3, override.aes = list(linewidth = 1.5))) +
  theme(legend.key.width = unit(1, "cm")) +
  theme(axis.text.x = element_text(angle = 45, 
                                   vjust = 1,
                                   hjust = 1
  ))
```
MASSIVE spike in Wandering and Unregistered complaint calls.

#### Break down the other three categories just because

```{r}
brisbane_clean %>% 
  group_by(date_range, category, animal_type) %>%
  filter(((year == 2016 & quarter == "Q4") | year > 2016) & animal_type == "Cat") %>%
  summarise(count = n()) %>% 
  filter(count > 5) %>% 
  ggplot(aes(x = date_range, y = count, colour = category, group = category)) +
  geom_line(linewidth = 1) +
  labs(title = "Reasons for Cat Complaint Calls, Brisbane Q4 2016 - Q2 2020",
       y = "No. of Calls",
       x = "Quarter, Year") +
  mytheme +
  scale_y_continuous(breaks = seq(0, 800, by = 50)) +
  guides(color = guide_legend(nrow = 3, override.aes = list(linewidth = 1.5))) +
  theme(legend.key.width = unit(1, "cm")) +
  theme(axis.text.x = element_text(angle = 45, 
                                   vjust = 1,
                                   hjust = 1
  ))

brisbane_clean %>% 
  group_by(date_range, category, animal_type) %>%
  filter(((year == 2016 & quarter == "Q4") | year > 2016) & animal_type == "Attack") %>%
  summarise(count = n()) %>% 
  filter(count > 5) %>% 
  ggplot(aes(x = date_range, y = count, colour = category, group = category)) +
  geom_line(linewidth = 1) +
  labs(title = "Reasons for Attack Complaint Calls, Brisbane Q4 2016 - Q2 2020",
       y = "No. of Calls",
       x = "Quarter, Year") +
  mytheme +
  scale_y_continuous(breaks = seq(0, 800, by = 50)) +
  guides(color = guide_legend(nrow = 3, override.aes = list(linewidth = 1.5))) +
  theme(legend.key.width = unit(1, "cm")) +
  theme(axis.text.x = element_text(angle = 45, 
                                   vjust = 1,
                                   hjust = 1
  ))

brisbane_clean %>% 
  group_by(date_range, category, animal_type) %>%
  filter(((year == 2016 & quarter == "Q4") | year > 2016) & animal_type == "Other Animal") %>%
  summarise(count = n()) %>% 
  filter(count > 5) %>% 
  ggplot(aes(x = date_range, y = count, colour = category, group = category)) +
  geom_line(linewidth = 1) +
  labs(title = "Reasons for Complaint Calls filed as \"Other\", Brisbane Q4 2016 - Q2 2020",
       y = "No. of Calls",
       x = "Quarter, Year") +
  mytheme +
  scale_y_continuous(breaks = seq(0, 800, by = 50)) +
  guides(color = guide_legend(nrow = 4, override.aes = list(linewidth = 1.5))) +
  theme(legend.key.width = unit(1, "cm")) +
  theme(axis.text.x = element_text(angle = 45, 
                                   vjust = 1,
                                   hjust = 1
  ))
```

### Suburb, type of animal, type of call

```{r}
brisbane_clean %>% 
  filter(((year == 2016 & quarter == "Q4") | year > 2016)) %>% 
  # filter(year > 2016 & year < 2020) %>%
  group_by(date_range, suburb, animal_type) %>% 
  summarise(count = n()) %>% 
  slice_max(count, n = 1) %>% 
  group_by(date_range, animal_type) %>% 
  summarise(count = n()) %>% 
  group_by(date_range) %>% 
  mutate(prop = scales::percent(round(count / sum(count), 2))) %>% 
  ggplot(aes(x = date_range, y = count, fill = animal_type)) +
  geom_col(position = "fill") +
  geom_text(aes(label = prop), position = position_fill(vjust = 0.5)) +
  mytheme +
  labs(title = "Proportion of Most Regular Call Type by Suburb, Brisbane, Q4 2016 - Q2 2020",
       y = "Proportion (%)",
       x = "Quarter, Year") +
  scale_y_continuous(labels = scales::percent) +
  guides(fill=guide_legend(nrow=1, override.aes = list(colour = "black",
                                                       size = 0.1))) +
  theme(legend.key.width = unit(1, "cm")) +
  theme(axis.text.x = element_text(angle = 45, 
                                   vjust = 1,
                                   hjust = 1
  )) +
  scale_fill_brewer(palette = "Set1")
```


# Townsville

Only dogs and cats!
Last 3 months of 2013 through first 6 2020

```{r}
townsville_clean %>% 
  filter(year != 2013 & year != 2020) %>% 
  group_by(year, animal_type, complaint_type) %>% 
  summarise(count = n()) %>% 
  arrange(year, -count)
```

## Questions

### Total call volume for complaint calls, trend over time

```{r}
townsville_clean %>% 
  group_by(date_range) %>% 
  summarise(count = n()) %>% 
  ggplot() +
  geom_line(aes(x = date_range, y = count, group = 1), linewidth = 1, colour = "chocolate1") +
  labs(title = "Total Call Volume, Animal Complaints, Townsville Q4 2013 - Q2 2020",
       y = "No. of Calls",
       x = "Quarter, Year") +
  mytheme +
  scale_y_continuous(breaks = seq(1000, 3000, by = 250)) +
  theme(axis.text.x = element_text(angle = 45, 
                                   vjust = 1,
                                   hjust = 1
  ))

townsville_clean %>% 
  group_by(date_range, animal_type) %>% 
  summarise(count = n()) %>% 
  ggplot() +
  geom_line(aes(x = date_range, y = count, colour = animal_type, group = animal_type), linewidth = 1) +
  labs(title = "Total Call Volume , Animal Complaints by Animal, Townsville Q4 2013 - Q2 2020",
       y = "No. of Calls",
       x = "Quarter, Year") +
  mytheme +
  scale_y_continuous(breaks = seq(0, 3000, by = 125)) +
  theme(axis.text.x = element_text(angle = 45, 
                                   vjust = 1,
                                   hjust = 1
  ))
```

### Particular call most common?

```{r}
townsville_clean %>% 
  group_by(date_range, animal_type) %>% 
  summarise(count = n()) %>% 
  ggplot() +
  geom_line(aes(x = date_range, y = count), linewidth = 1, group = 1, colour = "chocolate1") +
  labs(title = "Total Call Volume, Animal Complaints, Townsville Q4 2013 - Q2 2020",
       y = "No. of Calls",
       x = "Quarter, Year") +
  mytheme +
  theme(axis.text.x = element_text(angle = 45, 
                                   vjust = 1,
                                   hjust = 1)) +
  facet_wrap(~animal_type, scales = "free", nrow = 2)

townsville_clean %>% 
  group_by(date_range, complaint_type, animal_type) %>%
  filter(animal_type == "dog") %>%
  summarise(count = n()) %>% 
  filter(count > 5) %>% 
  ggplot(aes(x = date_range, y = count, colour = complaint_type, group = complaint_type)) +
  geom_line(linewidth = 1) +
  labs(title = "Reasons for Dog Complaint Calls, Townsville Q4 2013 - Q2 2020",
       y = "No. of Calls",
       x = "Quarter, Year") +
  mytheme +
  scale_y_continuous(breaks = seq(0, 800, by = 50)) +
  guides(color = guide_legend(nrow = 3, override.aes = list(linewidth = 1.5))) +
  theme(legend.key.width = unit(1, "cm")) +
  theme(axis.text.x = element_text(angle = 45, 
                                   vjust = 1,
                                   hjust = 1
  ))

townsville_clean %>% 
  group_by(date_range, complaint_type, animal_type) %>%
  filter(animal_type == "cat") %>%
  summarise(count = n()) %>% 
  filter(count > 5) %>% 
  ggplot(aes(x = date_range, y = count, colour = complaint_type, group = complaint_type)) +
  geom_line(linewidth = 1) +
  labs(title = "Reasons for Cat Complaint Calls, Townsville Q4 2013 - Q2 2020",
       y = "No. of Calls",
       x = "Quarter, Year") +
  mytheme +
  scale_y_continuous(breaks = seq(0, 800, by = 50)) +
  guides(color = guide_legend(nrow = 3, override.aes = list(linewidth = 1.5))) +
  theme(legend.key.width = unit(1, "cm")) +
  theme(axis.text.x = element_text(angle = 45, 
                                   vjust = 1,
                                   hjust = 1
  ))
```


### Suburb, type of animal, type of call



```{r}
townsville_clean %>% 
  group_by(date_range, suburb, complaint_type) %>% 
  summarise(count = n()) %>% 
  slice_max(count, n = 1) %>% 
  group_by(date_range, complaint_type) %>% 
  summarise(count = n()) %>% 
  group_by(date_range) %>% 
  mutate(prop = scales::percent(round(count / sum(count), 2))) %>% 
  ggplot(aes(x = date_range, y = count, fill = complaint_type)) +
  geom_col(position = "fill") +
  geom_text(aes(label = prop), position = position_fill(vjust = 0.5)) +
  mytheme +
  labs(title = "Proportion of Most Common Complaint by Suburb, Townsville, Q4 2013 - Q2 2020",
       y = "Proportion (%)",
       x = "Quarter, Year") +
  scale_y_continuous(labels = scales::percent) +
  guides(fill=guide_legend(nrow=1, override.aes = list(colour = "black",
                                                       size = 0.1))) +
  theme(legend.key.width = unit(1, "cm")) +
  theme(axis.text.x = element_text(angle = 45, 
                                   vjust = 1,
                                   hjust = 1
  )) +
  scale_fill_brewer(palette = "Set1")

townsville_clean %>% 
  filter(animal_type == "dog") %>% 
  group_by(date_range, complaint_type, suburb) %>%
  summarise(count = n()) %>% 
  group_by(date_range, complaint_type) %>% 
  slice_max(count) %>% 
  group_by(complaint_type, suburb) %>% 
  summarise(count = n()) %>% 
  arrange(complaint_type, -count) %>% 
  ggplot(aes(x = suburb, y = count, fill = complaint_type)) +
  geom_col() +
    mytheme +
  labs(title = "Suburb with Highest Quarterly Call Volume (Dogs), Townsville, Q4 2016 - Q2 2020",
       y = "Instances",
       x = "Suburb") +
  guides(fill=guide_legend(nrow=2, override.aes = list(colour = "black",
                                                       size = 0.1))) +
  theme(legend.key.width = unit(1, "cm")) +
  theme(axis.text.x = element_text(angle = 45, 
                                   vjust = 1,
                                   hjust = 1
  )) +
  scale_fill_brewer(palette = "Set1")

townsville_clean %>% 
  filter(animal_type == "cat") %>% 
  group_by(date_range, complaint_type, suburb) %>%
  summarise(count = n()) %>% 
  group_by(date_range, complaint_type) %>% 
  slice_max(count) %>% 
  group_by(complaint_type, suburb) %>% 
  summarise(count = n()) %>% 
  arrange(complaint_type, -count) %>% 
  ggplot(aes(x = suburb, y = count, fill = complaint_type)) +
  geom_col() +
  mytheme +
  labs(title = "Suburb with Highest Quarterly Call Volume (Cats), Townsville, Q4 2016 - Q2 2020",
       y = "Instances",
       x = "Suburb") +
  guides(fill=guide_legend(nrow=1, override.aes = list(colour = "black",
                                                       size = 0.1))) +
  theme(legend.key.width = unit(1, "cm")) +
  theme(axis.text.x = element_text(angle = 45, 
                                   vjust = 1,
                                   hjust = 1
  )) +
  scale_fill_brewer(palette = "Set1")

```

